Slitasje og kjørespor

### 2023-01-17 DRAFT_slitasjeOgKjørespor.Rmd
minor: switching branches

### Homogeneous impact areas

```{r, eval=F}
eaTools::ea_homogeneous_area(infra2)
```

>>>>

### Homogeneous impact areas
I want to use the [homogeneous impact areas]() to define smaller regions into which I can extrapolate the indicator values.

```{r}
HIA <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_agg.rds")
```

```{r}
tmap_mode("view")
tm_shape(HIA)+
  tm_polygons()
```
